02_DESeq_characterization

### 2019-11-22 analysis/03_DESeq2_characterization.Rmd
one more go term
now with endocrine

GOterms <- rbind(parentalbehavior, reproduction, behavior, systemdevelopment)

>>>>

endocrineprocess <- read.table("../results/goterms/endocrineprocess.txt", sep = "\t", row.names = NULL,  fill=TRUE)
endocrineprocess$GO <- "endocrine process, GO:0050886"

GOterms <- rbind(parentalbehavior, reproduction, behavior, systemdevelopment, endocrineprocess)
